
\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{etaremune}
\usepackage[gen]{eurosym}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

\usepackage{multicol}

% Set your name here
\def\name{Matthew DiGiuseppe}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://matthewdigiuseppe.com}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {political science, international relations, political economy},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.75em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}\\
{\large \href{http://www.matthewdigiuseppe.com}{matthewdigiuseppe.com} \\ }
% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.15in}

\begin{minipage}{0.75\linewidth}
  \href{https://www.universiteitleiden.nl/en/social-behavioural-sciences/political-science}{Universiteit Leiden} \\
  Associate Professor \\
  Institute of Political Science \\
  PO Box 9555
  2300 RB Leiden, Netherlands  \\
\end{minipage}
\begin{minipage}{0.75\linewidth}
  \begin{tabular}{ll}
    +1 (516) 582-2879 \\
    +31 6 18855616 \\
    \href{mailto:mdigiuseppe@gmail.com}{mdigiuseppe@gmail.com} \\
      &\\
  \end{tabular}
\end{minipage}

\section*{Employment History}
\begin{itemize}
	\item \emph{Universitair Hoofddocent (Associate Professor)} 2022 - Present \\
	Institute of Political Science, Universiteit Leiden 
	\item \emph{Universitair Docent 1 (Senior Assistant Professor w/ Tenure)} 2018- 2022 \\
	Institute of Political Science, Universiteit Leiden 
  \item \emph{Assistant Professor} 2012-2018  \\
  Department of Political Science, University of Mississippi \\
  \emph{Stopped tenure clock for one-year}
\end{itemize}

\section*{Education}

\begin{itemize}
  \item Ph.D. Political Science, Binghamton University, 2012\\ 
  M.A. Political Science, Binghamton University, 2010\\
   M.A. Government \& Politics, St. John's University, 2006\\
   B.S. Communications, St. John's University, 2004

\end{itemize}

\section*{Research Interests}
\begin{itemize}
\item	International \& Comparative Political Economy
\item 	International Sovereign Finance 
\item The Political Economy of Armed Conflict (Interstate \& Internal)
\end{itemize}

\section*{Grants}
	\begin{itemize}
    \item NWO XS (\euro 50,000) Political Polarization and Public Support for AI Governance
    \item European Research Council Starting Grant 2020-2025 (\euro{1.5} Million) for the Micro-foundations of Debt Crises Project 
    \item Leiden University KIEM-Una Europa Grant (2025).  With six other scholars. Used for survey experiments demonstrating the constraints sovereign debt imposes on climate change initiatives. (\euro10.000)
    \item Leiden University KIEM Grant (2023).  With four other scholars. Used for survey experiments demonstrating the constraints sovereign debt imposes on climate change initiatives. (\euro10.000)
	\item Global Transformations and Governance Challenges Seed Grant (2023).  With four other scholars. Used for survey experiments demonstrating the constraints sovereign debt imposes on climate change initiatives. (\euro10.000)
	\item Global Transformations and Governance Challenges Seed Grant (2020).  With four other scholars. Used for survey experiments demonstrating the constraints sovereign debt imposes on climate change initiatives. (\euro9.500)
	\item Summer Faculty Research Grant, University of Mississippi (2013, 2014, 2017 \& 2018) 
	\item Office of Research and Sponsored Programs at the University of Mississippi Investment Grant (\$2800 for a Survey Experiment)
	\item Southeastern (Athletic) Conference Faculty (SEC) Faculty Travel Grant (2015) 
	 \textit{Awarded by the College of Liberal Arts and Sciences, University of Mississippi}
	\item Dissertation Year Fellowship (2011-2012 Academic Year)\\
	\textit{Awarded by the Department of Political Science, Binghamton University}
	\item International Studies Association Travel Grant 2011 \\
	The Graduate School at Binghamton University Travel Grant 2011 \\
	American Political Science Association Travel Grant 2010	
\end{itemize}

\section*{Publications}

\begin{etaremune}

  \item \textbf{Putting the Public in Public Debt} (with Jaroslaw Kantorowicz, Bastián González-Bustamante, and Alessia Aspide) \emph{Conditional Accept} Public Choice


    \item \textbf{Scaling Open-ended Survey Responses Using LLM-Paired Comparisons} (with Michael E. Flynn) Forthcoming  \emph{Public Opinion Quarterly}

\item \textbf{The Mass Politics of Public Debt, Immigration, and Austerity} (with Alessia Aspide) Forthcoming \emph{Journal of European Public Policy} 


\item \textbf{Information, Uncertainty, \& Public Support for Brinkmanship during the 2023 Debt Limit Negotiations} (with Patrick Shea) Forthcoming \emph{British Journal of Political Science} 

\item \textbf{Financing Green Investments} (with Jarek Kantorwicz, Marrione Collewet, Henrik Vrijberg) 2024  \emph{Energy Policy} 184 - (Impact Factor 9) 

\item \textbf{Farming then Fighting: the relationship between idle time and social conflict} (w/ Roos van der Haer \& Babak Rezaee) Forthcoming \emph{Political Science Research and Methods} 

\item \textbf{Threats and the Public Constraint on Military Spending: A Survey Experiment in Italy} (with Alessia Aspide and Jordan M. Becker) Forthcoming \emph{The British Journal of Political Science}. 

\item \textbf {Ethnic Politics and Sovereign Credit} (with Kathleen Brown and Patrick Shea) Forthcoming \emph{Review of International Political Economy}. 

\item \textbf{Age and Public Support for Debt.} (w/ Alessia Aspidie, Kathleen Brown, \& Alexander Slaski). 2023 \emph{European Journal of Political Research} 62(4).

\item \textbf{Culture and European Attitudes on Public Debt } (w/ Alessia Aspidie, Kathleen Brown, \& Alexander Slaski). 2023 \emph{New Political Economy} 28(4).

\item \textbf{Do Consumers Follow the Flag?} (w/ Colin M. Barry) 2022 \emph{International Interactions} 48(6).

\item \textbf{The Wedding Bells of War: the influence of armed conflict on child marriages in West Africa} (with Roos van der Haer) 2023 \emph{Journal of Peace Research}

\item \textbf{U.S. Patronage, State Capacity, and Civil Conflict} (with Patrick Shea) 2022 \emph{Journal of Politics} 84 (2)

\item \textbf{Formal Alliances, Informal Signals \& Military Effort} (with Patrick Shea) 2021 \emph{European Journal of International Relations} 27 (4)

\item  \textbf{The Devil's Haircut: Investor-State Disputes over Debt Restructuring} (With Patrick Shea) 2019 at \emph{the Journal of Conflict Resolution} 63(8)

\item \textbf{Selling a Deal: Economics, Security, and Individual-level Preferences for Trade Agreements} (with Katja Kleinberg) 2019.   \emph{International Interactions} 45(2)

\item \textbf{Transparency, Risk \& FDI } (with Colin Barry) 2019. \emph{Political Research Quarterly} 72(1). 

\item \textbf{International Development NGOs and Bureaucratic Capacity: Facilitator or Destroyer?} (with Susanna Campbell and Amanda Murdie) 2019. \emph{Political Research Quarterly} 72(1).

\item \textbf{Divided Government, Sovereign Finance, and Government Survival in Democracies} (with Patrick Shea) 2018. \emph{Business \& Politics} 20(3). 

\item \textbf{Arms and Democratic Allies.} (with Paul Poast) 2018. \emph{The British Journal of Political Science} 48(4).
%Paper presented at the Annual Meeting of the American Political Science Association, Washington D.C., 2014 and the Peace Science Society Annual Meeting, Knoxville, TN, 2013 

\item \textbf{The Physical Consequences of Fiscal Flexibility: Sovereign Credit and Physical Integrity Rights} (with K. Chad Clay) 2017. \emph{the British Journal of Political Science} 47(4).

\item \textbf{Borrowed Time: Sovereign Finance, Regime Type \& Leader Survival } (with Patrick Shea) 2017.  \emph{Economics \& Politics} 28(3).
%Paper presented at the  Annual Convention of the American Political Science Association, Chicago, IL 2013.

 \item  \textbf{Guns, Butter and Debt: Sovereign Creditworthiness and Military Spending} 2015. \emph{Journal of Peace Research} 52(2).
 
\item \textbf{Sovereign Credit and the Fate of Leaders: Reassessing the Democratic Advantage} (with Patrick Shea) 2015. \emph{ International Studies Quarterly} 59(3): 557-570.

\item \textbf{The Fiscal Autonomy of Deciders: Creditworthiness and Conflict Initiation} 2015.  \emph{Foreign Policy Analysis} 11(3): 317-338.

\item \textbf{Tightening the Belt: Austerity and Alliance Formation} (with Michael A. Allen) 2013. \textit{International Studies Quarterly} 57(4): 647-659:  

\item \textbf{Good for the Money? International Finance, State Capacity and Internal Armed Conflict} (with Colin Barry and Richard Frank) 2012. {\it Journal
    of Peace Research} 49(3): 391-405.



\end{etaremune}

\section*{Research In Progress }

\subsection*{Revise \& Resubmit }
\begin{itemize}
\item \textbf{Perceived Political Bias in LLMs Reduces Persuasive Abilities} (with Josh Robison)

 \item \textbf{Information, Party Politics, and Public Support for Central Bank Independence} (with Ana Caroloina Garriga and Andreas Kern)	

    \item \textbf{Is the IMF a Scapegoat? A survey experiment in Kenya \& Ghana} (with Kathleen Brown, Rod Abouharb, and Bernhard Resinsberg)
    

 \end{itemize}

 
%\subsection*{Revise \& Resubmit}
%\begin{itemize}
%  \item \textbf{The New Fiscal Trillema} (With Alessia Aspide)

%\end{itemize}


\subsection*{Under Review}
\begin{itemize}

	 \item \textbf{Ad Machina: Partisanship and Support for Delegating Government Decisions to Autonomous Algorithms} (with Katrin Paula and Tobias Rommel)	
     \item \textbf{AI on the Battlefield?  Revisiting Public Support for LAWs} (with Katrin Paula and Tobias Rommel)	
	
     	 \item \textbf{The Partisan Bias in Inflation Expectations} (with Ana Caroloina Garriga and Andreas Kern)	
     \item \textbf{Bottom-Up Preferences for Public Debt Reduction and Repayment} (with Alessandro Del Ponte)	
  \item \textbf{External Threats and Support for International Cooperation} (with Jordan Becker, Haemin Jee, and Tongfi Kim)	





  
%\item \textbf{Discounting, Distribution, and Debt} (with Eric Arias and Patrick Shea)

\end{itemize}


%\subsection*{In Preparation}
%\begin{itemize}

%	 \item \textbf{Forecasting Debt Crises} (with Patrick Shea)

%	\item \textbf{Banking on Conflict: Funding Military Might with Unwitting Lenders} Paper presented at the annual meeting of the European Political Science Association, Belfast, U.K. 2019, the International Political Economy Society Meeting, Boston, MA 2018, and the Annual Meeting of the International Studies Association - Midwest, St. Louis, MO 2017, REPAL 2021.   
	% \item \textbf{The Micro-foundations of Debt Crises} (with Alexander Slaski \& Patrick Shea) Paper presented at the Annual Meeting of the American Political Science Association, San Francisco, CA 2017 \& the International Studies Association Conference, Toronto, 2018. 
% \end{itemize}



\subsection*{Invited Presentations}
\begin{itemize}

\item \textbf{Bottom Up Sovereign Debt Preferences} Politics of Finance Conference at Technical University of Munich in July 2023. 

\item \textbf{NATO strategic concept conference} U.S. Military Academy February 2022. 


\item \textbf{Banking on Conflict: Funding Military Might with Unwitting Lenders}. Speaker Series of the Department of Government, University of Essex, 2020 

\item \textbf{Divided Government, Sovereign Finance, and Government Survival in Democracies} (with Patrick Shea) \emph{Politics of Government Revenue Conference} organized by Kevin Morrison and Helen Milner. Princeton University, 2015.

\item \textbf{The Politics of Debt Restructuring: Institutions, Preferences, and Creditor Losses} (With Patrick Shea) University of Memphis, 2015.

\item \textbf{Divided Government, Sovereign Finance, and Government Survival in Democracies} (with Patrick Shea) \emph{The Political Economy of Risk Conference.} University of Houston, 2016.

\item \textbf{Military Expenditure, External Threats and Fiscal Consolidation: A Survey Experiment in Italy} (with Alessia Aspide and Jordan M. Becker) NATO Strategic Concept Conference in February 2022 at West Point, NY.  



\end{itemize}



\subsection*{Valorization}

\begin{itemize}
	\item 2022 - ``\href{https://theconversation.com/russia-faces-first-foreign-default-since-1918-heres-how-it-could-complicate-putins-ability-to-wage-war-in-ukraine-181139}{Russia faces its first default since 1918 - here's how it could complicate Putin's ability to wage war in Ukraine}'' published on \emph{The Conversation}
	\item 2022 - Invited to present at NATO Strategic Concept conference at the United States Military Academy (West Point, NY)
	\item 2018 - Niskanen Center's Science of Politics Podcast (2018)  \href{https://www.niskanencenter.org/episode-15-how-debt-finance-leads-to-war-and-defense-spending/}{(link)} 
 
 \end{itemize}




\subsection*{Unpublished Papers \& Conference Presentations}
\begin{itemize}



\item \textbf{Power Parity \& Trade } (with Nathan A. Andrew)  \\
Paper presented at the Annual Meeting of the Southern Political Science Association, New Orleans, LA 2017. 


\item \textbf{Foreign Aid and Private Goods: Finding Evidence of Capture with Trade Data}  \\
Paper presented at the Annual Meeting of the Midwest Political Science Association, Chicago, IL 2015,  the Annual Meeting of the International Studies Association, Atlanta, GA 2016, the Annual Meeting of the Southern Political Science Association, New Orleans, LA 2017. 

\item \textbf{Fiscal Space and Coercive Diplomacy }  \\
Paper presented at the Annual Meeting of the American Political Science Association, Philadelphia, PA 2016

\item \textbf{Fiscal Constraints and the Pursuit of Peace }  \\
Paper presented at the Annual Meeting of the International Studies Association, Toronto, Canada 2014.  \& the Annual Meeting of the International Studies Association, Atlanta, GA 2016. 

\item \textbf{``Propping up'' Leaders with US Foreign Aid} (with Michael E. Flynn)  \\
Paper presented at the Annual Meeting of the Midwest Political Science Association, Chicago, IL  2014. 

\item \textbf{Commodity Shocks, Shock Absorbers and Civil Conflict} (with Richard W. Frank)\\
Paper presented at the Annual Meeting of the American Political Science Association, Washington D.C., 2014


\item \textbf{Economic Competition and Labor Rights} (with K. Chad Clay and Colin M. Barry)  \\
Paper presented at the Annual Meeting of the International Studies Association, Toronto, Canada  2014 and the International Political Economy Society Meeting, Washington D.C., 2014.

\item \textbf{Out of the Frying Pan: INGOs, Economic Crises and Human Security} (with Amanda Murdie)  \\
Paper presented at the Annual Meeting of the Midwest Political Science Association, Chicago, IL  2014. 

\item \textbf{State Opposition: Separation, Simultaneity, and Sequential Causation in Terrorism and Civil Conflict} (with Michael A. Allen and Richard W. Frank) \\
Paper presented at the Midwest Political Science Conference (2013) and scheduled to be presented at the Annual Convention of the American Political Science Association (2012)

\item \textbf{Bullets and Bonds: International Sovereign Finance and Rivalry Behavior} \\
Paper presented at the Annual Meeting of the International Studies Association, Montreal, QC, Canada, 2011 \& the Annual Meeting of the Peace Science Society, Los Angeles, CA, 2011.

\item \textbf{A Good Friend Isn't Hard to Buy: Economic Interdependence and Alliance Reliability}\\
 Paper presented at the Annual Meeting of the American Political Science Association in Toronto, Ontario, Canada, 2009. 
 
%\item \textbf{Does Trade Foster Common Interests?} (with Benjamin O. Fordham)\\
%Paper presented at the Annual Meeting of the Mid-West Political Science Association in Chicago, IL. 2009. 

%\item \textbf{Trade and Conflict: A Strategic Approach} \\
%Paper presented at the Annual Meeting of the International Studies Association in New York, NY. 2009. 

\end{itemize}

\section*{Service to Discipline}
	\begin{itemize}
		\item Associate Editor \textit{International Studies Review} (2022-2026)
		\item Editorial Board Member of \textit{International Studies Review}
		\item Editorial Board Member of \textit{International Interactions}
		\item Reviewer for over 20 journals. 
		\item Els Witte PhD Prize Jury Member (2022, 2023)
	\end{itemize}
	

\section*{University Service}
\emph{Leiden University}
\begin{itemize}
	\item Director Post Graduate Studies (August 2023 - December 2025)
	\item Institute Board Member (August 2023 - December 2025)
	\item Direct Supervision of 6 instructors and support staff
	\item MSc Opleiding Commissie (Chair, September 2021-2023)
	\item MSc Opleiding Commissie (2019-present, Acting Chair July-October 2020)
	\item Research Committee (2021-2023)
	\item PhD Taskforce Member (2021-2022)
	\item PhD Supervision 
    \begin{itemize}
        \item  Successfully graduated:  Spielberger, Aspidie, Brown. Currently supervising
        \item  Currently supervising: Mirelmi , Akkerman, Slupski
    \end{itemize}
	\item Direct Supervision of 1 Post-doc
	\item Search Committee Chair: 3 UD in International Relations (2025)
    \item Search Committee Chair: 1 UD in Development Politics (2021)
	\item Search Committee Chair: 2 PhDs in IPE (2020)
	\item Search Committee Chair: 1 Post-Doc in IPE(2020)
	\item Search Committee Member: 5 UDs 2019 (2019)
	\item Search Committee Member: 1 UD in European Politics  (2019)
	\item Organizer of the Politics and Policy Pre Analysis Plan Workshop (ongoing)
\end{itemize}
\emph{University of Mississippi}
\begin{itemize}
	\item Graduate Admissions Committee
	\item PhD co-supervision (2 students)
	\item Search Committee Member (Assistant Professor)
\end{itemize}


\section*{Teaching Certificates \& Experience}


\begin{itemize}

\item Basis Kwalificatie Onderwijs (BKO), granted 2022 \\


\item \emph{Classes Taught at Leiden University:} \\ 

Economics for Political Science, Introduction to International Political Economy, International Political Economy, Foreign Policy in the Trump Era (Bachelor Project \& Seminar)

\item \emph{Classes Taught at University of Mississippi:}\\
Introduction to International Relations, Politics of the World Economy, International Conflict, Ethnic Conflict and International Terrorism, Global Political Economy (Graduate Seminar), Graduate Pro-Seminar in International Relations, Political Economy of Conflict (Honors Seminar), War in World Politics, Foreign Policy in the Trump Era (Honors Seminar). 

\item \emph{Classes Taught at Binghamton University:}\\
Political Economy of Armed Conflict, Domestic Forces in International Relations, Political Economy of International Economic Crises, Introduction to World Politics, International Political Economy	
\end{itemize}

	
%\section*{Professional Affiliations}
%\begin{itemize}
%\item American Political Science Association\\
%International Studies Association\\
%Mid-West Political Science Association\\
%International Political Economy Society\\
%\end{itemize}


\section*{Skills}

\subsection*{Languages}
\begin{itemize}
	\item English - Native Speaker
	\item Dutch - B1
\end{itemize}

\subsection*{Software}
\begin{itemize}
	\item R, Stata, SPSS, Latex
\end{itemize}



\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}

